### 2018-03-26 tex/paper.tex
Add explanation of web demo

\section{Visualising and interacting with contracts}
\label{section:tool}

\sjtnote{Pablo: can you add something here about the online visualisation, including one or more suitable screenshots? It might be worth giving a condensed screenshot of the whole screen, and then more detailed ones of parts of the display.}

\sjtnote{Should it have a name?}

In the next section we re-examine the model and the Marlowe language, looking at possible extensions, alternative design decisions and ways in which we can formally analyse Marlowe contracts.

>>>>

\section{Visualising and interacting with contracts}

\label{section:tool}

One of the objectives of Marlowe is to be accessible to a wider audience
than a general purpose language would. With this aim, and to aid Marlowe's
usage by people that does not know is not familiar with its syntax,
we have developed a web tool that supports the interactive construction,
edition, and simulation of smart-contracts written in Marlowe. The
tool is publicly available in the url: \url{https://input-output-hk.github.io/scdsl/}.
In Figure~\ref{fig:full-screenshot-demo}, we provide a screenshot
of the tool in the middle of simulating the execution of the ``incentivised
saving'' contract described in Section~\ref{section:example}.

The tool has been mainly written in Haskell and compiled to JavaScript
by the Haste compiler \plsnote{Citation needed}, it also relies on
the Blockly library \plsnote{Citation needed} for providing a visual
editor for smart contracts written in Marlowe. Blockly's editor allows
the user to visualise and edit smart-contracts as interlocking blocks
that can be dragged and dropped like pieces of a jigsaw puzzle (see
Figure~\ref{fig:detail-of-block}). The tool also provides functionality
to generate syntactically correct and formatted code (that is displayed
in the upper right corner of the application), and to convert the
code back to its block representation.

\begin{figure}
\begin{centering}
\includegraphics[width=1\textwidth]{pix/screenshot1}
\par\end{centering}
\caption{\label{fig:full-screenshot-demo}Screenshot of the visualisation tool
running the incentivised deposit contract.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail1}\caption{\label{fig:detail-of-block}Detail of five interlocked 
blocks.}
\end{figure}

The execution of complete contracts can be simulated block by block
by using the panel on the right (see Figure~\ref{fig:detail-of-interface}),
which includes text fields to view and edit the current block number,
the state of the contract, the current inputs, and the outputs from
last block.

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail2}\caption{\label{fig:detail-of-interface}Detail of the interface for 
contract
execution simulation.}
\end{figure}

Additionally, to facilitate the introduction of inputs, the tool provides
two different interfaces:
\begin{itemize}
\item The manual interface (see Figure~\ref{fig:detail-of-manual-interface}),
provides a template for each of the four possible types of input:
commits, redeems, payment claims, and choices.
\item The smart interface (see Figure~\ref{fig:detail-of-smart-interface}),
calculates the possible operations that would make sense given the
current inputs, state of the contract, block number, and remaining
contract; and it provides them in a table with most of the parameters
already filled in.
\end{itemize}
\begin{figure}
\begin{centering}
\includegraphics[scale=0.7]{pix/detail3}
\par\end{centering}
\caption{\label{fig:detail-of-manual-interface}Detail of the manual interface.}
\end{figure}

\begin{figure}
\centering{}\includegraphics[scale=0.7]{pix/detail4}\caption{\label{fig:detail-of-smart-interface}Detail of the smart 
interface.}
\end{figure}

The smart interface is usually more convenient to use than the manual
interface since the later provides between 3 and 4 fields for each
operation whereas the former ``guesses'' the possible intentions
of the user and usually can input new operations with a single click
(except for choices, which still may require the user to input a number).
